EGGs are adhesive!

### 2025-05-26 calco/finalArxiv.tex
versione arxiv

\noindent
\parbox{11.4cm}{
\begin{restatable}{lemma}{comp}\label{prop:eqhyp_complete}
Consider a diagram $F\colon \D \to \EqHyp$ and let $(E_D, V_D, Q_D, s_D, t_D, q_D)$ be the image of an object $D$. Then the following hold
\begin{enumerate}
		\item $F$ has a colimit, which is preserved by $K$;
	\item consider a cone $(L, \{l_D\}_{D\in \D})$ limiting  for $K \circ F$ and let $((E, V), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ be one for $T\circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a {\color{red} mono $m\colon Q\mto L$} such that the diagram on the right commutes for every $D\in \D$.
\end{enumerate}
\end{restatable}}\hfill 
\parbox{3cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_D}}

@@

\begin{definition} We say that an object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{labelled e-hypergraph} if $\mathcal{H}$ is an e-hypergraph. We define the category $\egg_\Sigma$ as the full subcategory of $\EqHyp_\Sigma$ given by labelled e-hypergraphs. We denote {\color{red} by $J_\Sigma$} the corresponding inclusion functor .
\end{definition}

@@

Let $\pbe_\Sigma$ be the class of morphisms in $\egg_\Sigma$ whose image in $\egg$ lies in $\pbe$. Notice that $\pbe_\Sigma$ is also the class of arrows whose image through $J_\Sigma$ is in $\pbc_\Sigma$.
%
By \Cref{thm:slice-functors} we get the following result.

@@

\noindent 
\parbox{7.5cm}{\begin{remark}
	Now that we have put all the structures of this work in place, it is worthwhile to give a visual map of all the categories that we have discussed/introduced and of the relationships between them. We will use the curved arrows to denote full and faithful inclusions.
\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{j_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}

@@

\begin{center}\xymatrix{        
 \begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
                \node[style=node](v1) at (-0.9, 0.3){};
                \node[style=node](v2) at (-0.9, -0.3){};
                \node[style=medium box] at (0, 0){$/$};
                \node[style=none](divfst) at (-0.3, 0.3){};
                \node[style=none](divsnd) at (-0.3, -0.3){};
                \node[style=none](divout) at (0.3, 0){};
                \node[style=node] (w) at (0.9, 0){};
        \end{pgfonlayer}        
        \begin{pgfonlayer}{edgelayer}
                \draw(v1) to (divfst.center);
                \draw(v2) to (divsnd.center);
                \draw(divout.center) to (w);
        \end{pgfonlayer}
        \begin{pgfonlayer}{eqlayer}
                \draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
                \end{pgfonlayer}\begin{pgfonlayer}{background}
                        \draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
                \end{pgfonlayer}
        \end{tikzpicture}
	\ar@{=>}[r] &
        \begin{tikzpicture}[baseline=(nil.center)]\begin{pgfonlayer}{nodelayer}
                \node[style=node](v1) at (-0.9, 0.3){};
                \node[style=node](v2) at (-0.9, -0.3){};
                \node[style=medium box] at (0, 0){$/$};
                \node[style=none](divfst) at (-0.3, 0.3){};
                \node[style=none](divsnd) at (-0.3, -0.3){};
                \node[style=none](divout) at (0.3, 0){};
                \node[style=node] (w) at (0.9, 0){};
                \node[style=small box] at (0, -1){$1$};
                \node[style=none](one) at (0.3, -1){};
                \node[style=node](z) at (0.9, -1){};
                \node[style=none](nil) at (0, -0.5){};
        \end{pgfonlayer}        
        \begin{pgfonlayer}{edgelayer}
                \draw(v1) to (divfst.center);
                \draw(v2) to (divsnd.center);
                \draw(divout.center) to (w);
                \draw(one.center) to (z);
        \end{pgfonlayer}
        \begin{pgfonlayer}{eqlayer}
                \draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
                \draw[dashed, rounded corners](0.6, 0.3) rectangle (1.2, -1.3);
        \end{pgfonlayer}\begin{pgfonlayer}{background}
                        \draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
        \end{pgfonlayer}\end{tikzpicture}
}
\end{center}

@@

%\interlinepenalty 1000
\bibliography{biblio}

>>>>

\noindent
\parbox{11.4cm}{
\begin{restatable}{lemma}{comp}\label{prop:eqhyp_complete}
Consider a diagram $F\colon \D \to \EqHyp$ and let $(E_D, V_D, Q_D, s_D, t_D, q_D)$ be the image of an object $D$. Then the following hold
\begin{enumerate}
		\item $F$ has a colimit, which is preserved by $K$;
	\item consider a cone $(L, \{l_D\}_{D\in \D})$ limiting  for $K \circ F$ and let $((E, V), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ be one for $T\circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $D\in \D$.
\end{enumerate}
\end{restatable}}\hfill 
\parbox{3cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_D}}

@@

\begin{definition} We say that an object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{labelled e-hypergraph} if $\mathcal{H}$ is an e-hypergraph. We define the category $\egg_\Sigma$ as the full subcategory of $\EqHyp_\Sigma$ given by labelled e-hypergraphs. We denote by $Z_\Sigma$ the corresponding inclusion functor .
\end{definition}

@@

Let $\pbe_\Sigma$ be the class of morphisms in $\egg_\Sigma$ whose image in $\egg$ lies in $\pbe$. Notice that $\pbe_\Sigma$ is also the class of arrows whose image through $Z_\Sigma$ is in $\pbc_\Sigma$.
%
By \Cref{thm:slice-functors} we get the following result.

@@

\noindent 
\parbox{7.5cm}{\begin{remark}
	Now that we have put all the structures of this work in place, it is worthwhile to give a visual map of all the categories that we have discussed/introduced and of the relationships between them. We will use the curved arrows to denote full and faithful inclusions.
\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}

@@

\begin{center}
\hspace{.5cm}
\xymatrix{        
 \begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
                \node[style=node](v1) at (-0.9, 0.3){};
                \node[style=node](v2) at (-0.9, -0.3){};
                \node[style=medium box] at (0, 0){$/$};
                \node[style=none](divfst) at (-0.3, 0.3){};
                \node[style=none](divsnd) at (-0.3, -0.3){};
                \node[style=none](divout) at (0.3, 0){};
                \node[style=node] (w) at (0.9, 0){};
        \end{pgfonlayer}        
        \begin{pgfonlayer}{edgelayer}
                \draw(v1) to (divfst.center);
                \draw(v2) to (divsnd.center);
                \draw(divout.center) to (w);
        \end{pgfonlayer}
        \begin{pgfonlayer}{eqlayer}
                \draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
                \end{pgfonlayer}\begin{pgfonlayer}{background}
                        \draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
                \end{pgfonlayer}
        \end{tikzpicture}
	\ar@{=>}[r] &
        \begin{tikzpicture}[baseline=(nil.center)]\begin{pgfonlayer}{nodelayer}
                \node[style=node](v1) at (-0.9, 0.3){};
                \node[style=node](v2) at (-0.9, -0.3){};
                \node[style=medium box] at (0, 0){$/$};
                \node[style=none](divfst) at (-0.3, 0.3){};
                \node[style=none](divsnd) at (-0.3, -0.3){};
                \node[style=none](divout) at (0.3, 0){};
                \node[style=node] (w) at (0.9, 0){};
                \node[style=small box] at (0, -1){$1$};
                \node[style=none](one) at (0.3, -1){};
                \node[style=node](z) at (0.9, -1){};
                \node[style=none](nil) at (0, -0.5){};
        \end{pgfonlayer}        
        \begin{pgfonlayer}{edgelayer}
                \draw(v1) to (divfst.center);
                \draw(v2) to (divsnd.center);
                \draw(divout.center) to (w);
                \draw(one.center) to (z);
        \end{pgfonlayer}
        \begin{pgfonlayer}{eqlayer}
                \draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
                \draw[dashed, rounded corners](0.6, 0.3) rectangle (1.2, -1.3);
        \end{pgfonlayer}\begin{pgfonlayer}{background}
                        \draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
        \end{pgfonlayer}\end{tikzpicture}
}
\end{center}

@@

\interlinepenalty 1000
\bibliography{biblio}
